Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-22 papers/ms.tex
update ms

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$\alpha$, defined such that the group member with the smallest core
distance has $\alpha=1$, the group member with the greatest core
distance has $\alpha=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry,\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$.}
this procedure yields $\alpha \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with weight exceeding 0.02 as gray points, and
overplot 4{,}763 objects with weights exceeding 0.10 as black points.
The previously known $\delta$~Lyr\ cluster is visible at
$(l,b)=(68^\circ,15^\circ$) and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.
RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5
,-3.5 )\mkms$.  Most of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this 
 yielded 11 known false positives, 6 ``confirmed'' planets, and 8
 ``candidate'' planets.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.\footnote{These figures
yield an estimate of the size of Cep-Her: if our 4/14
matches represent the true positive rate, then
multiplying by the number of stars above our weight threshold
(12{,}436) yields $\approx$3{,}500 stars in the complex.  
This might however be an under-count,
since Kepler observed sparse 
regions of the complex, which are expected to have higher
contamination rates (Figure~\ref{fig:XYZvtang}, top panel).}

>>>>

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$\alpha$, defined such that the group member with the smallest core
distance has $\alpha=1$, the group member with the greatest core
distance has $\alpha=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry,\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$.}
this procedure yields $\alpha \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $\alpha>0.02$ as gray points, and
overplot 4{,}763 objects with $\alpha>0.10$ as black points.
The previously known $\delta$~Lyr\ cluster is visible at
$(l,b)=(68^\circ,15^\circ$) and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.
RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5
,-3.5 )\mkms$.  Most of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this 
 yielded 11 known false positives, 6 ``confirmed'' planets, and 8
 ``candidate'' planets.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.
%\footnote{These figures
%yield an estimate of the size of Cep-Her: if our 4/14
%matches represent the true positive rate, then
%multiplying by the number of stars above our weight threshold
%(12{,}436) yields $\approx$3{,}500 stars in the complex.  
%This might however be an under-count,
%since Kepler observed sparse 
%regions of the complex, which are expected to have higher
%contamination rates (Figure~\ref{fig:XYZvtang}, top panel).}
